FHJ: A Formal Model for Hierarchical Dispatching and Overriding

### 2018-05-29 ECOOP18/sections/Overview.tex
expanded text for discussing diamond problem with figure 3 (d)(e)(f)

In  Figure~\ref{fig:examplesmbody}, (a) is the base case for unintentional conflicts, namely the \wordfork{} inheritance. (b) uses overriding to explicitly merge the conflicting methods. (c) represents hierarchical overriding. (d) and (e) are two base cases of diamond inheritance in \MIM{} and the definition of each $C$ is rejected because $T$ is an ambiguous parent to $C$. (f) gives a common solution to the diamond as in Java or traits, which is to explicitly override $A.m$ and $B.m$ in $C$. In the last three examples, conflicting methods $A.m$ and $B.m$ should be viewed as
intentional conflicts, as they come from the same source $T$.
% Similar to many OO languages, the model also allows \textit{super
% method invocation} in a method body. The invocation
% \lstinline|super.T::m()| will ignore all the subtypes of
% \lstinline|T|, and only look at \lstinline|T| together with its
% super interfaces. It should behave the same as \lstinline|new
% T().m()| in principle.

\bruno{I remember that a big complain in the reviews was talking about
diamond inheritance. The Figure does have diamond inheritance but this
wasn't clear to the reviewers. Please expand the text to emphasize
diamond inheritance better!}

>>>>

In  Figure~\ref{fig:examplesmbody}, (a) is the base case for unintentional conflicts, namely the \wordfork{} inheritance. (b) uses overriding to explicitly merge the conflicting methods. (c) represents hierarchical overriding. Our model supports diamond inheritance and can deal with diamond problems. For example, (d) and (e) are two base cases of diamond inheritance in \MIM{} and the definition of each $C$ is rejected because $T$ is an ambiguous parent to $C$. One solution for diamond inheritance is to merge methods coming from different parents. (f) gives a common solution to the diamond as in Java or traits, which is to explicitly override $A.m$ and $B.m$ in $C$. And our calculus supports this kind of merging methods. In the last three examples, conflicting methods $A.m$ and $B.m$ should be viewed as
intentional conflicts, as they come from the same source $T$.
% Similar to many OO languages, the model also allows \textit{super
% method invocation} in a method body. The invocation
% \lstinline|super.T::m()| will ignore all the subtypes of
% \lstinline|T|, and only look at \lstinline|T| together with its
% super interfaces. It should behave the same as \lstinline|new
% T().m()| in principle.

\bruno{I remember that a big complain in the reviews was talking about
diamond inheritance. The Figure does have diamond inheritance but this
wasn't clear to the reviewers. Please expand the text to emphasize
diamond inheritance better!}\yanlin{expanded.}
